### 2016-04-19 Manuscript/SW_early_life_telomeres.Rmd
DSR edits

Cox regression showed no effect of individual-level or cohort-level RTL on survival later in life (individual-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL+Agemonths+frailty(FieldPeriodID))))$coefficients[1,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL+Agemonths+frailty(FieldPeriodID))))$coefficients[1,6])`; cohort-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL*Agemonths+RTL+frailty(FieldPeriodID))))$coefficients[1,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL*Agemonths+RTL+frailty(FieldPeriodID))))$coefficients[1,6])`), and no interaction between RTL and age on survival (individual-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,6])`). $\Delta$RTL was not related to longer-term survival (estimate `r round3(summary(coxph(with(subset(subset(Loss,LayYear<2008),Agemonths == 1),Surv(RemainingLife2+1,Died)~Loss)))$coefficients[1,1])`, P = `r round3(summary(coxph(with(subset(subset(Loss,LayYear<2008),Agemonths ==1 ),Surv(RemainingLife2+1,Died)~Loss)))$coefficients[1,5])`).

>>>>

Cox regression showed no effect of individual-level or cohort-level RTL on survival later in life (individual-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL+Agemonths+frailty(FieldPeriodID))))$coefficients[1,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL+Agemonths+frailty(FieldPeriodID))))$coefficients[1,6])`; cohort-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL*Agemonths+RTL+frailty(FieldPeriodID))))$coefficients[1,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~cohortTL*Agemonths+RTL+frailty(FieldPeriodID))))$coefficients[1,6])`), and no interaction between RTL and age on survival (individual-level: estimate = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,1])`, P = `r round2(summary(coxph(with(juv9,Surv(Lifespan,Died)~RTL*Agemonths+frailty(FieldPeriodID))))$coefficients[4,6])`). $\Delta$RTL was not related to longer-term survival (estimate `r round3(summary(coxph(with(subset(Loss,LayYear<2008),Surv(RemainingLife2+1,Died)~Loss+Agemonths)))$coefficients[1,1])`, P = `r round2(summary(coxph(with(subset(Loss,LayYear<2008),Surv(RemainingLife2+1,Died)~Loss)))$coefficients[1,5])`).

### 2016-04-19 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
DSR edits

```{r Figure 5}
temp <- subset(juv13,Agemonths != 1)
temp$LayYear <- factor(temp$LayYear)
temp[,'Survived to following year?'] <- ifelse(temp$SurvivedNext == 1,'Y','N')

Fig4B <- ggplot(temp,
       aes(x = LayYear,
           y = RTL,
           fill = `Survived to following year?`)) +
  xlab('Cohort') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_boxplot(outlier.shape = NA,alpha = 0.2)+
  geom_jitter(aes(col = `Survived to following year?`),position=position_jitterdodge(jitter.width = 0.2))+
  annotate('text',x = 0.5,y = 1.5,label = 'B')

Fig4B

>>>>

```{r Figure 5}
temp <- juv
temp$LayYear <- factor(temp$LayYear)
temp[,'Survived to following year?'] <- ifelse(temp$SurvivedNext == 1,'Y','N')
temp[,'Age (months)'] <- factor(temp$Agemonths)

Fig5 <- ggplot(temp,
       aes(x = RTL,
           y = SurvivedNext,
           fill = `Age (months)`,
           col = `Age (months)`)) +
  xlab('RTL') +
  ylab('Proportion survived')+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'top') +
  geom_point(alpha=0.2)+
  stat_smooth(method = 'glm',family = 'binomial')+
    scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  scale_fill_manual(values = c('grey','darkorange','darkgreen'))

pdf('Figures/Figure 5.pdf',
    width = 4,
    height = 4,
    paper = 'a4')
Fig5
dev.off()
